SPIN Novelty

### 2019-04-20 stats/kids_novelty.Rmd
update kids novelty

d <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep",
         trial != "train1", trial != "train2")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F),
         experiment = condition)%>%
  select(-pick_src)

@@

d <- bind_rows(d_raw, d_mcc)

>>>>

d_spin <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep",
         trial != "train1", trial != "train2")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F),
         experiment = condition)%>%
  select(-pick_src)

@@

d <- bind_rows(d_spin, d_mcc)
